Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-11-13 manuscript/main.tex
more more more

\usepackage{scicite}
% Clean citations with biblatex
\usepackage[
backend=biber,
style=numeric,
maxbibnames=50
]{biblatex}

@@

@@

All data needed to evaluate the conclusions in the paper
are present in the paper and/or the Supplementary Materials.
Taxonomic and functional microbial profiles, as well as subject
demographics necessary for statistical analyses and machine learning are
available on the Data Dryad
\cite{bonhamDataDryad2023}.
Data processing, generation of summary statistics, and
generation of plots was performed using the julia programming language
and 3rd party packages
\cite{bezansonJuliaFreshApproach2017,bonhamMicrobiomeJlBiobakeryUtils2021,danischMakieJlFlexible2021,blaomMLJJuliaPackage2020,ben_sadeghi_2022_7359268,dahua_lin_2023_7695673,douglas_bates_2023_7734970}.
Information for replicating the package environment
as well as code for data analysis and figure generation, as well as scripts for automated
download of input files are available on GitHub at https://github.com/KlepacCerajLab/Resonance,
and archived on Zenodo \cite{kevin_bonham_2023_7647510}.

>>>>

\usepackage{scicite}
% Clean citations with biblatex
\usepackage[
backend=biber,
style=numeric,
maxbibnames=100
]{biblatex}

@@

Members of the RESONANCE consortium also contributed to
project planning, conceptualization, and funding acquisition.

@@

All data needed to evaluate the conclusions in the paper
are present in the paper and/or the Supplementary Materials.
Taxonomic and functional microbial profiles, as well as subject
demographics necessary for statistical analyses and machine learning are
available on the Data Dryad
\cite{bonhamDataDryad2023}.
Data processing, generation of summary statistics, and
generation of plots was performed using the julia programming language
and 3rd party packages
\cite{bezansonJuliaFreshApproach2017,bonhamMicrobiomeJlBiobakeryUtils2021,danischMakieJlFlexible2021,blaomMLJJuliaPackage2020,ben_sadeghi_2022_7359268,dahua_lin_2023_7695673,douglas_bates_2023_7734970}.
Information for replicating the package environment
as well as code for data analysis and figure generation, as well as scripts for automated
download of input files are available on GitHub at https://github.com/Klepac-Ceraj-Lab/Resonance,
and archived on Zenodo \cite{kevin_bonham_2023_7647510}.
